\section{Day 4}
\subsection{Lecture 1}

\noindent \textit{Disclaimer: today had a lot of spectral sequences, and I'm not sure how coherent the writing is below here. I tried to get the spectral sequences correct, but I may have missed some important language helping us make these.}

Yesterday we computed a homotopy fixed point spectral sequence. Suppose that $C_2\acts\calE$ where $\calE$ is a spectrum. 

$$E_2^{s,t} = H^s(C_2;\pi_t \calE)\Rightarrow \pi_{t-s}\calE^{hC_2}.$$

\DeclareSseqGroup\etatowertwo{}{
    \class[rectangle](0,0)
    \foreach\i in {1,...,11}{
        \class[fill = white](\i,\i)
        \structline(\i-1,\i-1,-1)(\i,\i,-1)
    }
}
\begin{sseqdata}[name = HFPSSd2,x range ={0}{16},y range = {0}{4},xscale = .5,Adams grading]
    \foreach \k in {-2,...,4}{
        \etatowertwo({4*\k},0)
    }
    \d[wongorange]3 (-4,0)
    \replacesource[rectangle]
    \d[wongorange]3(4,0)
    \replacesource[rectangle]
    \d[wongorange]3(12,0)
    \replacesource[rectangle]
    \foreach \n in {1,...,6}{
        \d[wongorange]3 ({-4+\n},\n)
        \d[wongorange]3({4+\n},\n)
        \d[wongorange]3({12+\n},\n)
    }
\end{sseqdata}
\begin{center}
    \printpage[name = HFPSSd2]

    \printpage[name = HFPSSd2,page = 4]
\end{center}

The final $E_\infty$ page is $\pi_\ast E^{hC_2}$. This gives $\pi_\ast E = \mZ[u^{\pm 1}]$ where $\abs{u} =2$. (If this were a polynomial ring where $x$ is a variable, then $u$ would have the same weight the $x^2$ ``part.'')

\begin{question}{}{}
    How do we compute $\pi_\ast(E^{hC_2}\wedge V(0))$. 
\end{question}
There is a spectral sequence $$\underbrace{E_2^{s,t} = H^s(C_2,\pi_t(E\wedge V(0)))}_{\text{Question 1}}\Rightarrow \underbrace{\pi_{t-s}E^{hC_2}\wedge V(0)}_{\text{Question 2}}$$

For Question 1, we have 
\begin{align*}
    \mS&\xr{2}\mS\to V(0)\tag{fiber sequence}\\
    E\wedge \mS&\xr{2}E\wedge \mS \to E\wedge V(0)\tag{fiber sequence}
\end{align*}
This induces a long exact sequence in homotopy groups. 
\begin{center}
  \begin{tikzcd}[ampersand replacement = \&]
    \&\cdots\ar[r]\&\pi_{k+1}(E\wedge V(0))\ar[dll,out = 225,in = 45]\\ 
    \pi_k(E\wedge \mS)\ar[r,"2"]\& \pi_k(E\wedge \mS)\ar[r]\& \pi_k(E\wedge \mS)\ar[dll,out = 225,in = 45]\\ 
    \pi_{k-1}(E\wedge \mS)\ar[r,"2"]\& \cdots.
  \end{tikzcd}
\end{center}
After following the LES (using our spectral sequence $E_\infty$ page on the the previous page), we get $$\pi_t(E\wedge V(0)) = \begin{cases}
    \mZ/2 & t\text{ even}\\
    0 & t\text{ odd}
\end{cases}.$$
Therefore, our $E_2^{s,t}$ group we were looking for is coming from $$H^s(C_2,\pi_t(E\wedge V(0))).$$

\begin{center}
    \begin{tikzcd}[ampersand replacement = \&]
      \&\cdots\ar[r]\&\pi_{3}(E\wedge V(0))\ar[dll,out = 225,in = 45]\\ 
      \pi_2(E\wedge \mS)\ar[r,"2","u\mapsto 2u"']\& \pi_2(E\wedge \mS)\ar[r]\& \pi_2(E\wedge \mS)\ar[dll,out = 225,in = 45]\\ 
      \pi_{1}(E\wedge \mS)\ar[r,"2"]\& \pi_1(E\wedge \mS)\ar[r]\& \pi_1(E\wedge \mS)\ar[dll,out = 225,in = 45]\\ 
      \pi_{0}(E\wedge \mS)\ar[r,"2"]\& \pi_0(E\wedge \mS)
    \end{tikzcd}
\end{center}

Here, we need to find $H^s(C_2;\pi_2(E\wedge V(0)))$ and put this into an Adams grading. This means the $x$-axis doesn't represent $t$ but rather represents $t-s$.  When you do this computation, we get the following picture for the $E_2$ page. 
\DeclareSseqGroup\tenamwednesday{}{
    \foreach\k in {0,4}{
        \foreach \j in {0,...,6}{
            \class[fill = white]({\k+\j},\j)
        }
    }
    \foreach\k in {2,6}{
        \foreach \j in {0,...,6}{
            \class[circlen=2,wongpink,fill = wongpink]({\k+\j},\j)
        }
    }
    }

\begin{sseqdata}[name = EwedgeV0,Adams grading]
        \tenamwednesday(0,0)
        \tenamwednesday(-8,0)
        \tenamwednesday(8,0)
\end{sseqdata}
\begin{center}
    \printpage[name=EwedgeV0,x range = {0}{16}, y range = {0}{6},xscale =.75,grid = chess]
\end{center}
The pink dot represents the module $\mZ/2\sets{u}$ and the white dot represents the module $\mZ/2\sets{1}$. The map $E\xr{\by 2}E\to E\wedge V(0)$ as maps of spectra induces a long exact sequence in $\pi_\ast$ which in this case is a short exact sequence! $$0\to \pi_{2t}E\to \pi_{2t}E\to \pi_{2t}E\wedge V(0)\to 0$$ $$0\to \pi_{\ast}E\to \pi_{\ast}E\to \pi_{\ast}E\wedge V(0)\to 0.$$
\begin{fact}{}{}
    A short exact sequence of modules $$0\to M'\to M\to M''\to 0$$ induces a long exact sequence in group cohomology, $$\cdots \to H^{s-1}(G;M'')\to H^s(G;M')\to H^s(G;M)\to H^s(G;M'')\to H^{s+1}(G;M')\to \cdots.$$
\end{fact}
Now, since we have the ses in modules $$0\to \pi_\ast(E)\to\pi_\ast(E)\to\pi_\ast(E\wedge V(0))\to 0,$$ we get the LES in group cohomology $$\cdots \to H^s(G;\pi_\ast E)\to \underbrace{H^s(G;\pi_\ast E)}_{E_2^{s,\ast}(E)}\to \underbrace{H^s(G,\pi_\ast E\wedge V(0))}_{E_2^{s,\ast}(E\wedge V(0))}\to \textcolor{wongpink}{\underbrace{H^{s+1}(G;\pi_{\ast}E)}_{E_2^{s+1,\ast}(E)}}\to \cdots.$$ Since the elements are inside of our spectral sequences, we actually get maps between spectral sequences! This now tells us information about our differentials between the different spectral sequences!

\newpage
\subsection{Lecture 2}

Again, we'll use this spectral sequence
\begin{center}
    \printpage[name=EwedgeV0,x range = {0}{16}, y range = {0}{6},xscale =.75,grid = chess]
\end{center}
and the maps 
$$\cdots \to H^s(G;\pi_\ast E)\to \underbrace{H^s(G;\pi_\ast E)}_{E_2^{s,\ast}(E)}\to \underbrace{H^s(G,\pi_\ast E\wedge V(0))}_{E_2^{s,\ast}(E\wedge V(0))}\to \textcolor{wongpink}{\underbrace{H^{s+1}(G;\pi_{\ast}E)}_{E_2^{s+1,\ast}(E)}}\to \cdots.$$

From this les in cohomology, we can see that the spectral sequences associated to each piece converge at $E_\infty$ to the long exact sequence $$\cdots \to \pi_{t-s}E^{hG}\to \pi_{t-s}E^{hG}\to \pi_{t-s}E^{hG}\wedge V(0)\to \pi_{t-s-1}E^{hG}\to \cdots.$$

The question which started out at the beginning of the lecture was (effectively) this: 
\begin{question}{}{}
    What is a morphism of spectral sequences? If we have a LES in cohomology which induces a map for spectral sequences, how can we say this generally?
\end{question}

\begin{remark}{Method 1}
    Let's look at the LES sequence, 
    \begin{center}
      \begin{tikzcd}[ampersand replacement = \&]
        \overset{0}{\pi_{6}E^{hC_2}}\ar[r,"2"]\& \overset{0}{\pi_{6}E^{hC_2}}\ar[r]\& \pi_{6}E^{hC_2}\wedge V(0)\ar[dll,out = 225,in = 45]\\  
        \overset{0}{\pi_{5}E^{hC_2}}\ar[r,"2"]\& \overset{0}{\pi_{5}E^{hC_2}}\ar[r]\& \pi_{5}E^{hC_2}\wedge V(0)\ar[dll,out = 225,in = 45]\\ 
        \overset{\mZ}{\pi_{4}E^{hC_2}}\ar[r,"2"]\&\overset{\mZ}{\pi_{4}E^{hC_2}}\ar[r]\&\pi_{4}E^{hC_2}\wedge V(0)\ar[dll,out = 225,in = 45]\\ 
        \pi_{3}E^{hC_2}\ar[r]\& \cdots
      \end{tikzcd}.
    \end{center}
    This means that $\pi_6(E^{hC_2}\wedge V(0)) = 0$ and $\pi_5(E^{hC_2}\wedge V(0))=0.$
\end{remark}

\begin{fact}{}{}
    If we're given an exact sequence $$A\xr{f}B\to C\to D\xr{g}E,$$ where these are $\mZ/2$-modules (i.e. $\mZ/2$ vector spaces), then $C\cong \coker f\oplus \ker g$. 
\end{fact}

\begin{theorem}{}{}
    Let $G$ be a finite group. If $E^{hG}$ satisfies the property that there is a number $P$, called the period, such that for any $n$ $$\pi_{n+P}(E^{hG}) = \pi_{n}(E^{hG}),$$ then if $M$ is a finite complex\footnote{suspension spectrum of a finite CW complex is an instance of this} $\pi_\ast(E^{hF}\wedge M)$ satisfies the same periodic property with period $p\leq P$ and this period is a factor of this number. 
\end{theorem}
This should convince us that our result is going to be something less than or equal to 8-periodic since $E^{hC_2}$ is 8-periodic. 
 

\begin{remark}{Method 2 for calculating spectral sequences}{}
    The second method goes as follows. 
    \begin{center}
          \begin{tikzcd}[ampersand replacement = \&]
            E_3^{s,t}(E^{hC_2})\ar[r,"f"]\ar[d,"d_3"']\ar[dr,phantom,"\circlearrowleft"]\& E_3^{s,t}(E^{hC_2}\wedge V(0))\ar[d,"d_3"]\\
            E_3^{s+3,t+2}(E^{hC_2})\ar[r,"f"']\& E_3^{s+3,t+2}(E^{hC_2}\wedge V(0))
          \end{tikzcd}
    \end{center}
    This is commutative, so in other words, if $x$ is in the top left corner, we require $$d_3(f(x)) = f(d_3(x))$$
\end{remark}