\documentclass{article}
\usepackage{spectralsequences}

\usepackage{geometry,hyperref}
\geometry{margin=1in}

\begin{document}

    Visit \href{https://mirror.math.princeton.edu/pub/CTAN/graphics/pgf/contrib/spectralsequences/manual/spectralsequencesmanual.pdf}{this link} for the documentation.

    \noindent Exercise 1 (Harder, try last! Test out your skills with the package, not a real spectral sequence): 

    Make the following diagram on your own. (Hint: I'm on page 0, using cohomological Serre grading, and I used a for loop to make my life easier.) What is the $E_4$ page of this spectral sequence? Why does Scotty like the $E_4$ page?

    \begin{sseqdata}[name = Exercise 1, cohomological Serre grading]
        \foreach \x in {0,...,5}{
            \foreach \y in {0,...,5}{
                \class(\x,\y)
            }
        }
        \d0(1,4)
        \d0(1,1)
        \d0(0,0)
        \d1(2,5)
        \d1(4,5)
        \d1(4,3)
        \d2(0,2)
        \d2(0,4)
        \d3(0,3)
        \d3(1,3)
        \d3(0,5)
        \class(2,3)
    \end{sseqdata}
    \begin{center}
        \printpage[name = Exercise 1,page = 0]
    \end{center}
    % \printpage[name = Exercise 1,page = 6]

    \medskip
    \hrule
    \medskip

    \noindent Exercise 2 (Start here!)

    Make the following diagram on your own! (Hint: I'm on page 0, using Adams grading, and I used some loops plus math to make my life easier)

    \begin{sseqdata}[name = ex2,Adams grading]
        \foreach \x in {0,...,5}{
            \foreach \y in {0,...,5}{
                \class({2*\x},\y)
            }
        }
    \end{sseqdata}
    \begin{center}
        \printpage[name = ex2,page = 0]
    \end{center}
    Question: What differentials have a chance to be supported here? Remember, we're using Adams grading!


    \newpage

    \noindent Exercise 3:

    What differentials could be supported on this spectral sequence using the Adams grading? Note that the scaling is different between the two axes!

    \begin{sseqdata}[name = ex3,Adams grading, yscale = .4]
        \foreach \x in {0,...,10}{
            \foreach \y in {0,...,10}{
                \class (\x,{2*\y})
            }
        }
    \end{sseqdata}
    \begin{center}
        \printpage[name = ex3,page =0]
    \end{center}

    \medskip
    \hrule
    \medskip

    \noindent Exercise 4
    
    Create this spectral sequence page 0 with Adams grading!

    \DeclareSseqGroup\tower{}{
        \class (0,0)
        \foreach \i in {1,...,5}{
            \class (0,\i)
            \structline(0,{\i-1},-1)(0,\i,-1)
        }
    }
    \DeclareSseqGroup\diagonal{}{
        \tower(0,0)
        \foreach\i in {1,...,5}{
            \class(\i,\i)
            \structline(\i-1,\i-1,-1)(\i,\i,-1)
        }
    }
    \begin{sseqdata}[name = ex4,Adams grading]
        \tower[blue](3,0)
        \diagonal[red](1,0)
        \class["2",rectangle] (0,0)
        \class["Scotty"] (0,1)
        \class["Z/2"] (0,3)
        \class[circlen =3] (0,4)
    \end{sseqdata}
    \begin{center}
        \printpage[name = ex4,x range = {0}{4},y range = {0}{4}]
    \end{center}

    \noindent Exercise 5: 

    Create a spectral sequence with Adams grading using differentials going from 0 to 3 to make some dots in a pattern that is your first initial. 
\end{document}